---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# storywranglr

<!-- badges: start -->
[![](https://www.r-pkg.org/badges/version/storywranglr?color=green)](https://cran.r-project.org/package=storywranglr)
<!-- badges: end -->

This package makes it easy to explore trends in Twitter data using the Storywrangler application programming interface (API). Data is returned in a tidy tibble to make it easy to work with and visualize.

For more details about Storywrangler, please see:

* API documentation: <https://github.com/janeadams/storywrangler>
* Academic paper describing uses: <https://advances.sciencemag.org/content/7/29/eabe6534.full>

## Installation

You can install the developer version, which has the latest bugfixes and features, with:

``` r
devtools::install_github("chris31415926535/storywranglr")
```

You can install the released version of storywranglr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("storywranglr")
```

## Examples

Let's use `storywranglr::ngrams()` to chart the popularity of the 2-gram "black friday" over time. Not surprisingly, it looks like there's an annual peak around Black Friday.

```{r example_ngram, message = FALSE, warning = FALSE}
library(storywranglr)
library(tidyverse)

result <- storywranglr::ngrams("black friday")

result %>%
  ggplot(aes(x=date, y=rank)) +
  geom_point() +
  theme_minimal() +
  scale_y_continuous(trans = "reverse") +
  labs(title = "Twitter rank popularity of 2-gram 'black friday'",
       subtitle = "Data from Storywrangler ngrams API",
       x = "Date",
       y = "Rank")


```

Now using `storywrangler::zipf()`, let's find the 10 top 2-grams from January 6, 2021. "the Capitol" made the top 10, and if we got a longer list we could expect to see other thematically related terms.

```{r example}
result <- zipf("2021-01-06", max = 10, ngrams = 2)

knitr::kable(result)
```
